Evaluation of classical correlation functions from 2/3D images on CPU and GPU architectures: introducing CorrelationFunctions.jl

### 2021-07-08 paper-correlations.tex
New shitplots

Our package takes one-, two- or three-dimensional arrays of any element type
(usually we restrict ourselves to integer numbers of type \code{Int} or
\code{Int8}) and treats them as homogeneous anisotropic media.

@@

With the \code{Map} module we follow the same procedure. Many functions in
\code{Map} can utilize Nvidia's GPUs using the CUDA library. For example,
two-point correlation function uses FFT transform optimized for Nvidia GPUs and
provided in \code{CUDA.FFT} package. We provide execution times for bot CPU and
GPU. The choice between CPU or GPU version is made depending on type of input
array. If it's \code{CuArray} rather than generic \code{AbstractArray} then CUDA
implementation is chosen.

>>>>

Our package takes one-, two- or three-dimensional arrays of any element type
(usually we restrict ourselves to integer numbers of type \code{Int} or
\code{Int8}) and treats them as homogeneous anisotropic media. The package can
understand two-phase as well as multiphase systems. Indeed, a multiphase system
$A$ can be easily converted to a two-phase system $B$ by applying an indicator
function $\chi(x)$ to each element of $A$ which can be written as $B = \chi(A)$.

@@

With the \code{Map} module we follow the same procedure. Many functions in
\code{Map} can utilize Nvidia's GPUs using the CUDA library. For example,
two-point correlation function uses FFT transform optimized for Nvidia GPUs and
provided in \code{CUDA.FFT} package. We provide execution times for both CPU and
GPU. The choice between CPU or GPU version is made depending on type of input
array. If it's \code{CuArray} rather than generic \code{AbstractArray} then CUDA
implementation is chosen. Please note, that CPU versions are much slower, so we
choose a different sides of squares ($s = 700, 1350, \dots, 7000$) and cubes
($s = 10, 45, \dots, 350$) for evaluation of the performance.
